---
title: "2019 Policy Reconsideration RIA Results"
date: "August, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(here)
library(knitr)
source(here("scripts", "setup.R"))

knitr::opts_chunk$set(
  echo = FALSE
  )

# scenario data in scope from calling env
if (!exists("scn_comps")) stop("Please render tables by running analysis script.")

scn_comp <- scn_comps[["opt1-prb"]]

# set some knitr options
options(knitr.table.format = 'html')

wb <- loadWorkbook("../output/xlsx/tables_policy_review.xlsx")

```

## Introduction

This document provides a partial results for the 2019 Policy Review RIAresults. This is an html document which can be viewed in your browser. Matching xlsx output tables are also produced.

**Technical note:** this document can be reproduced by knitting the rmarkdown code in R.

```{r}
#Summary Output Sheets "raw" totals by year
write_tbl_to_xlsx(scn_summ_list[["opt1-prb"]], wb, "opt1-prb")
write_tbl_to_xlsx(scn_summ_list[["opt1-crb"]], wb, "opt1-crb")
```


## Overview of Affected Facilities

Affected facilities for the purpose of RIA tables are facilities which make changes in their controls as a result of this reconsideration action. In the case of this framework, this corresponds to differences in the total counts of model-plant fate in particular years. 

Incrementally affected facilities means that vintage == year, e.g., facilities new/modified in a particular year that are affected.


```{r tbl_fac_affected}
tbl_fac_affected <- scn_comp_table(scn_comp,
              var_list = list("fac_affected"),
              row_detail = "total",
              show_years = 2019:2025)

tbl_incr_affected <- scn_comp %>%
  filter(year == vintage) %>%
  scn_comp_table(var_list = list("fac_affected"),
                 row_detail = "total",
                 show_years = 2019:2025) %>%
  rename(incr_affected = fac_affected)

tbl_affected <- left_join(tbl_incr_affected,   tbl_fac_affected, by = "year")

tbl_affected %>%
  mutate_at(.vars = c("incr_affected", "fac_affected"), funs(rndmark(., 2))) %>%
  kable(caption = "Affected Facility Overview Compared to 2018 Proposed Regulatory Baseline") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(columns = 1)

tbl_affected %>%
  write_tbl_to_xlsx(wb, "fac_affected")
```

```{r tbl_emissions}

tbl_emissions <- scn_comp_table(scn_comp,
               var_list = list("Methane", "VOC", "HAP", "CH4_CO2e"),
               row_detail = "total",
               show_years = 2014:2025)

tbl_emissions %>%
  mutate_at(.vars = c("Methane", "VOC", "HAP", "CH4_CO2e"), 
            funs(rndmark(., 2))) %>%
  kable(caption = "Change in Emissions for the Proposed Reconsideration Option compared to 2018 Proposed Regulatory Baseline, by year") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(columns = 1)

tbl_emissions %>% 
  write_tbl_to_xlsx(wb, "emissions")

```


```{r tbl_gas}

tbl_gas <- scn_comp_table(scn_comp,
               var_list = list("gas_capture", "gas_revenue"),
               row_detail = "total",
               show_years = 2019:2025)


tbl_gas %>%
  mutate(gas_capture = rndmark(gas_capture, 2),
         gas_revenue = currency(gas_revenue, 2)) %>%
  kable(caption = "Change in Natural Gas Recovery (Mcf) for the Proposed Reconsideration Option Compared to 2018 Proposed Regulatory Baseline, by year") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F)

tbl_gas %>%
  write_tbl_to_xlsx(wb, "gas_revenue")

```

```{r tbl_costs}

tbl_costs <- scn_comp_table(scn_comp,
               var_list = list("capital_cost", "ann_7", "gas_revenue", "ann_7_wgas"),
               row_detail = "total",
               show_years = 2019:2025)


tbl_costs %>%
  mutate_at(c("capital_cost", "ann_7", "gas_revenue", "ann_7_wgas"),
            .funs = funs(Mdollar(.))) %>%
  kable(caption = "Change in Natural Gas Recovery (Mcf) for the Proposed Option Compared to 2018 Proposed Regulatory Baseline, by year")

tbl_costs %>%
  write_tbl_to_xlsx(wb, "costs")

```


```{r comp_alts}

comp_alts <- scn_combo %>%
  filter(pol_scn %in% 
           c("1.opt1-prb", "2.opt1-crb")) %>%
  filter(year %in% c(2020,2025)) %>%
  group_by(pol_scn, year) %>%
  summarize_at(.vars = vars("Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  ungroup()

var_order <- c("Methane", "VOC", "gas_capture", "capital_cost", "ann_7", "ann_7_wgas")

comp_alts_vert <- comp_alts %>%
  mutate_at(c("Methane", "VOC", "gas_capture"), funs(rndmark(., 2))) %>%
  mutate_at(c("capital_cost", "ann_7", "ann_7_wgas"), funs(Mdollar(., 2))) %>%
  
  gather(var, value, "Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas") %>%
  spread(pol_scn, value) %>% 
  mutate(var = factor(var, levels = var_order)) %>%
  arrange(year, var)

comp_alts_vert %>%
  kable(caption = "Comparison of Proposed Option to 2018 Proposed Regulatory Baseline and Current Policy Baseline, 2020 and 2025") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(c(1))

comp_alts %>%
  
  gather(var, value, "Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas") %>%
  spread(pol_scn, value) %>% 
  mutate(var = factor(var, levels = var_order)) %>%
  arrange(year, var) %>%
  
  write_tbl_to_xlsx(wb, "comp_alts")

```

```{r comp_alts_context}
comp_alt_baselines <- scn_combo_context %>%
  filter(year %in% c(2020,2025)) %>%
  group_by(pol_scn, year) %>%
  summarize_at(.vars = vars("Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  ungroup()

var_order <- c("Methane", "VOC", "gas_capture", "capital_cost", "ann_7", "ann_7_wgas")

comp_alt_baselines_vert <- comp_alt_baselines %>%
  mutate_at(c("Methane", "VOC", "gas_capture"), funs(rndmark(., 2))) %>%
  mutate_at(c("capital_cost", "ann_7", "ann_7_wgas"), funs(Mdollar(., 2))) %>%
  
  gather(var, value, "Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas") %>%
  spread(pol_scn, value) %>% 
  mutate(var = factor(var, levels = var_order)) %>%
  arrange(year, var)

comp_alt_baselines_vert %>%
  kable(caption = "Comparison of Proposed Option from Multiple Baselines, 2020 and 2025") %>%
  kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
  collapse_rows(c(1))

comp_alt_baselines %>%
  
  gather(var, value, "Methane", "VOC", "gas_capture", 
                            "capital_cost", "ann_7", "ann_7_wgas") %>%
  spread(pol_scn, value) %>% 
  mutate(var = factor(var, levels = var_order)) %>%
  arrange(year, var) %>%
  
  write_tbl_to_xlsx(wb, "comp_alt_baselines")

```

```{r altbaselines}

tbl_altbaselines <- scn_combo_context %>%
  filter(year %in% c(2020, 2025)) %>%
  group_by(year, pol_scn) %>%
  summarize_at(.vars = vars("fac_affected", "Methane", "VOC", "capital_cost", "ann_7_wgas"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  ungroup()

tbl_altbaselines %>%
 kable(format.args = list(big.mark = ',', scientific = FALSE))

tbl_altbaselines %>% write_tbl_to_xlsx(wb, "altbaselines")

```

```{r costs_dr}

costs_dr <- scn_comp_table(scn_comp,
               var_list = list("ann_7", "gas_revenue", "ann_7_wgas", "ann_3", "ann_3_wgas"),
               row_detail = "total",
               show_years = 2019:2025) %>%
  
  mutate(gas_rev2 = gas_revenue) %>%
  select(year, ann_7, gas_revenue, ann_7_wgas, ann_3, gas_rev2, ann_3_wgas)
  

costs_dr %>%
  mutate_at(vars(-year), funs(Mdollar(., 2))) %>%
  kable(caption = "Undiscounted Annualized Cost Changes using 3 and 7 Percent Discount Rates Compared to 2018 Proposed Regulatory Baseline (million 2016$)")

costs_dr %>%
  write_tbl_to_xlsx(wb, "discount_rate")

```

```{r detail_tabs}

opt_yr_combo <- crossing(opt = 1:2, year = c(2020, 2025)) %>%
  mutate(optname = case_when(
    opt == 1 ~ "1.opt1-prb",
    opt == 2 ~ "2.opt1-crb")
  ) %>% select(opt, optname, year)


det_tab <- pmap_chr(opt_yr_combo, ~glue("Detail_{..2}_{..3}"))

tabfun <- function(scn_combo, opt, optname, year) {
  scn_comp <- scn_combo %>%
    filter(pol_scn == optname) %>%
    select(-pol_scn)
  
  maintab <- scn_comp_table(scn_comp,
              var_list = list("fac_affected", "Methane", "VOC", "HAP", "CH4_CO2e", "capital_cost", "annual_cost", "gas_revenue", "ann_7_wgas"),
              row_detail = "source",
              show_years = c(year)) 
  
  tottab <- scn_comp_table(scn_comp,
              var_list = list("fac_affected", "Methane", "VOC", "HAP", "CH4_CO2e", "capital_cost", "annual_cost", "gas_revenue", "ann_7_wgas"),
              row_detail = "total",
              show_years = c(year)) %>%
    mutate(year = "Total")
  
  result <- bind_rows(maintab, tottab)
    
  result
}



det_tabs <- pmap(opt_yr_combo, ~tabfun(scn_combo, ..1, ..2, ..3))

walk2(det_tabs, det_tab, ~write_tbl_to_xlsx(.x, wb, .y))

kabletab <- function(df, cap) {
  df %>%
    mutate_at(c("fac_affected", "Methane", "VOC", "HAP", "CH4_CO2e"),
              funs(rndmark(., 2))) %>%
    mutate_at(c("capital_cost", "ann_7_wgas"),
              funs(currency(., 2))) %>%
    kable(caption = cap) %>%
    kable_styling(bootstrap_options = c("condensed"), full_width = F) %>%
    collapse_rows(c(1,2))
}   

det_names <- pmap_chr(opt_yr_combo, ~glue("Detail of Affected Units, Proposed Option,  {..2}, {..3}"))

kabletab(det_tabs[[1]], det_names[[1]])
kabletab(det_tabs[[2]], det_names[[2]])
kabletab(det_tabs[[3]], det_names[[3]])
kabletab(det_tabs[[4]], det_names[[4]])

```

```{r eav_undiscounted}
cost_undisc_7 <- table_cost_disc_pv_eav(scn_comp, .07, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"), disc_flag = FALSE)

write_tbl_to_xlsx(cost_undisc_7, wb)

cost_undisc_3 <- table_cost_disc_pv_eav(scn_comp, .03, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"), disc_flag = FALSE)

write_tbl_to_xlsx(cost_undisc_3, wb)
```

```{r eav_disc}
cost_disc_7 <- table_cost_disc_pv_eav(scn_comp, .07, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"))

write_tbl_to_xlsx(cost_disc_7, wb)

cost_disc_3 <- table_cost_disc_pv_eav(scn_comp, .03, list("capital_cost", "annual_cost", "ann_r", "gas_revenue", "ann_r_wgas"))

write_tbl_to_xlsx(cost_disc_3, wb)
```

```{r pv_eav_combo}
totals_combo <- scn_combo %>%
  group_by(pol_scn) %>%
  summarize_at(.vars = vars("Methane", "VOC", "gas_capture"),
               .funs = funs(sum(., na.rm = TRUE))) %>%
  gather(var, value, Methane, VOC, gas_capture) %>%
  spread(pol_scn, value) %>%
  mutate(vartype = "Total")

pv_combo <- scn_combo %>%
  group_by(pol_scn, year) %>%
  summarize_at(vars("capital_cost", "ann_7", "ann_7_wgas"), 
               funs(sum(.))) %>%
  summarize_at(.vars = vars("capital_cost", "ann_7", "ann_7_wgas"),
               .funs = funs( sum(npv_xy_pmts(as.numeric(year), ., .07, 2016)) ))

eav_combo <- pv_combo %>%
  mutate_at(.vars = vars("capital_cost", "ann_7", "ann_7_wgas"),
            .funs = funs(equiv_annualized_value(., 7, .07, 0)))

pv_eav_combo_partial <- bind_rows(
  mutate(pv_combo, vartype = "PV"),
  mutate(eav_combo, vartype = "EAV")
) %>%
  gather(var, value, capital_cost, ann_7, ann_7_wgas) %>%
  spread(pol_scn, value)

pv_eav_combo <- bind_rows(
  totals_combo,
  pv_eav_combo_partial
) %>%
  mutate(vartype = factor(vartype, levels = c("Total", "PV", "EAV"))) %>%
  mutate(var = factor(var, levels = c("Methane", "VOC", "gas_capture", "capital_cost", "ann_7", "ann_7_wgas"))) %>%
  arrange(vartype, var) %>%
  select(var, vartype, everything())

pv_eav_combo
write_tbl_to_xlsx(pv_eav_combo, wb)
```

```{r dr_pv_eav}
dr_pv_eav <- bind_cols(
  table_cost_disc_pv_eav(scn_comp, .07, list("ann_r", "gas_revenue", "ann_r_wgas")),
  table_cost_disc_pv_eav(scn_comp, .03, list("ann_r", "gas_revenue", "ann_r_wgas"))
)

dr_pv_eav
write_tbl_to_xlsx(dr_pv_eav, wb)
```


```{r tsd}

tsd_opt_yr_combo <- crossing(opt = 1:2, year = c(2019:2025)) %>%
  mutate(optname = case_when(
    opt == 1 ~ "1.opt1-prb",
    opt == 2 ~ "2.opt1-crb")
  ) %>% select(opt, optname, year)

tsd_det_tab <- pmap_chr(tsd_opt_yr_combo, ~glue("Detail_{..2}_{..3}"))

tsdtabfun <- function(scn_combo, opt, optname, year) {
  scn_comp <- scn_combo %>%
    filter(pol_scn == optname) %>%
    select(-pol_scn)
  
  maintab <- scn_comp_table(scn_comp,
              var_list = list("fac_affected", "Methane", "VOC", "ann_7", "ann_7_wgas"),
              row_detail = "detail",
              show_years = c(year)) 
  
  tottab <- scn_comp_table(scn_comp,
              var_list = list("fac_affected", "Methane", "VOC", "ann_7", "ann_7_wgas"),
              row_detail = "total",
              show_years = c(year)) %>%
    mutate(year = "Total")
  
  result <- bind_rows(maintab, tottab)
    
  result
}



tsd_det_tabs <- pmap(tsd_opt_yr_combo, ~tsdtabfun(scn_combo, ..1, ..2, ..3))

tsd_wb <- loadWorkbook("../output/xlsx/tsd_policy_review.xlsx")
walk2(tsd_det_tabs, tsd_det_tab, ~write_tbl_to_xlsx(.x, tsd_wb, .y))

saveWorkbook(tsd_wb, "../output/xlsx/tsd_policy_review.xlsx", overwrite = TRUE)

```



```{r}
saveWorkbook(wb, "../output/xlsx/tables_policy_review.xlsx", overwrite = TRUE)



```


